\section{Security and Non-outsourcability}

\RH{Let's extend this section to security and nonoutsourcability justification, which extends Miller's paper.
In particular, we list/reformalise desired properties that can render pooled mining impossible. This should inlcude: Correctness, Feasibility, Parallelisability, Imcompressibility, Nonoutsourcability (we should reformalise this one), Non-transferability, .
}

\cite{miller2015nonoutsourceable} first formally defines cryptocurrency mining as scratch-off puzzles. \TODO{describe}

\begin{description}
    \item[Correctness] Any valid hash can be verified.
    \item[Feasibility] Mining is computationally feasible.
    \item[Parallelisability] The mining process can be parallelised.
    \item[$\mu$-Imcompressibility] The adversary cannot accelerate the mining process using pre-generated pairs of nonces and hashes, by at most a factor $\mu$ ($\mu \geq 1$). If $\mu = 1$, $\mathsf{Work}$ is the optimal way to mine.
    \item[Non-transferability] Given a block template, the adversary cannot accelerate the mining process using other valid hashes on this block template.
\end{description}

In addition, \cite{miller2015nonoutsourceable} introduces non-outsourceable scratch-off puzzles, and formally defines two levels of non-outsourcability, namely:

\begin{description}
    \item[Weak Non-outsourcability] If the pool operator outsources the mining process, miners can always steal the reward of mining.
    \item[Strong Non-outsourcability] In addition to the Weak Non-outsourcability, the pool operator cannot link the stolen mining reward to the miner who steals it.
\end{description}



Here, we introduce a variant of non-outsourceability: if the pool operator outsources the mining process (i.e., miners cannot mine in the name of the pool operator), in addition to the block template, he should show the private key associated with the public key in the coinbase transaction as well.
\TODO{more}

% need private key
As shown in appendix~\ref{vrf_standardised_construction}, both $\mathsf{VRFHash}$ and $\mathsf{VRFProve}$ take secret key $sk$ as input.
That is to say, if a pool operator would like to provide pooled mining service and let miners participate, he will need to provide miners with his secret key.

% none would like to provide private key
However, none rational pool operator will tend to give out his secret key, as revealing his secret key give others the opportunity to redeem his balance or forge his identity.

Therefore, following our construction, we eliminate the intentionality of pooled mining and can reduce the centralisation of mining power significantly.
