\documentclass[runningheads]{llncs}

\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{interval}
\usepackage{amsmath, amssymb}
\usepackage{cuted, tcolorbox}
\usepackage{tikz}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{algpseudocode}

\usepackage[normalem]{ulem}

\makeatletter
\newcommand{\printfnsymbol}[1]{%
  \textsuperscript{\@fnsymbol{#1}}%
}
\makeatother

\newcommand{\RH}[1]{\textcolor{blue}{#1}}
\newcommand{\JS}[1]{\textcolor{red}{#1}}
\newcommand{\TODO}[1]{\textcolor{red}{TODO: #1}}
\newcommand{\HY}[1]{\textcolor{brown}{#1}}

% blue comment
\newcommand\mycommfont[1]{\footnotesize\ttfamily\textcolor{blue}{#1}}
\SetCommentSty{mycommfont}
% blue triangle
\SetKwComment{Comment}{\color{blue} $\triangleright$\ }{}

\begin{document}

\title{VRF-based mining: How to rule out mining pools from blockchain ecosystem?}
\titlerunning{VRF-based mining}

\author{
    Runchao Han\thanks{equal contribution}\inst{1,2}
    \and Haoyu Lin\printfnsymbol{1}
    \and Jiangshan Yu\inst{1}
}
\authorrunning{Han et al.}

\institute{Monash University \and CSIRO-Data61}

\maketitle

\begin{abstract}
  In this paper, we describe VRF-based mining, a simple and effective way of making pooled mining impossible.
  Instead of using hash functions, VRF-based mining uses Verifiable Random Functions (VRFs) for Proof-of-work (PoW)-based consensus.
  As VRF binds the authorship with hashes, a pool operator should reveal his private key to outsource the mining process to miners, and miners can easily steal cryptocurrency in the pool operator's wallet anonymously.
  
  In addition, we informally revisit the definition of non-outsourceability in existing research, and show VRF-based mining achieves stronger non-outsourceability than all existing proposals.
  Moreover, we describe how to instantiate VRFs for VRF-based mining.
  Last, we discuss potential problems of having no mining pools, and how to address them.
  \keywords{Blockchain \and Cryptocurrency mining \and Mining pool.}
\end{abstract}

\input{sections/1intro.tex}
\input{sections/2preliminaries.tex}
\input{sections/3vrf-based-mining.tex}
\input{sections/4non-outsourceability.tex}
\input{sections/5instantiating-vrf.tex}
\input{sections/6problems-and-solutions.tex}
\input{sections/7related-work.tex}
\input{sections/8conclusion.tex}

\bibliographystyle{splncs04}
\bibliography{refs}

\appendix
\input{sections/999appendix.tex}

\end{document}